Covariates analysis of MSBB RNASeq data of region BM 36

### 2016-05-01 code/Rmd/MSSM_BM_36_RNASeq.Rmd
Added markdown to process BM 36

---
title: "Covariates analysis of MSBB RNASeq data of region BM 44"
author: "Thanneer Perumal"
date: "`r date()`"
output: html_document
---
```{r knit2synapse, eval=FALSE}
library(synapseClient)
library(knitr)
library(githubr)

@@

knit2synapse::knitToFolderEntity(file = "./MSSM_BM_44_RNASeq.Rmd",
                                 parentId ="syn5570248",
                                 entityName = 'MSBB BM 44 RNASeq')
```

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
# Synapse parameters
parentId = 'syn5570248';
activityName = 'Covariate analysis';
activityDescription = 'Covariate analysis of MSBB BM 44 RNASeq samples';

thisFileName <- 'MSSM_BM_44_RNASeq.Rmd'

# Github link
thisRepo <- getRepo(repository = "th1vairam/Brain_Reg_Net", ref="branch", refName='AMPAD')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/Rmd/',thisFileName))
```
Data were obtained from AMP-AD portal of MSSM, and following brain regions were analysed for differential expression between case and control:
  | Region | Name                        | 
  | :----- | --------------------------- | 
  | BM_44  | inferior frontal Gyrus (IFG)|

* BM 44: pars opercularis (of the inferior frontal gyrus), and it refers to a subdivision of the frontal region of cerebral cortex.

@@

METADATA = left_join(METADATA %>%
  dplyr::mutate(ID = gsub('hB_RNA_','',NewBarcode),
                ID = as.numeric(ID)),
  METADATA_TECHNICAL %>%
  dplyr::select(BB, BM.44.Barcode, BM36.Fnl, BM22.Fnl, BM10.Fnl, PMI, RACE, 
                AOD, CDR, SEX, NP.1, PlaqueMean, bbscore) %>%
  dplyr::rename(BM_44 = BM.44.Barcode,
                BM_10 = BM10.Fnl,
                BM_22 = BM22.Fnl,
                BM_36 = BM36.Fnl) %>%
  tidyr::gather(BrainRegion, ID, -BB, -PMI, -RACE, 
                -AOD, -CDR, -SEX, -NP.1, -PlaqueMean, -bbscore) %>%
  filter(!is.na(ID)) %>%
  dplyr::mutate(ID = as.numeric(ID))) %>%
  dplyr::filter(BrainRegion == 'BM_44')
rownames(METADATA) = METADATA$NewBarcode

@@

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = "MSBB BM 44 RNASeq", parentId = parentId)
CODE <- synStore(CODE)

>>>>

---
title: "Covariates analysis of MSBB RNASeq data of region BM 36"
author: "Thanneer Perumal"
date: "`r date()`"
output: html_document
---
```{r knit2synapse, eval=FALSE}
library(synapseClient)
library(knitr)
library(githubr)

@@

knit2synapse::knitToFolderEntity(file = "./MSSM_BM_36_RNASeq.Rmd",
                                 parentId ="syn5570248",
                                 entityName = 'MSBB BM 36 RNASeq')
```

@@

```{r synapse.parameters, include=FALSE, cache=TRUE}
# Synapse parameters
parentId = 'syn5570248';
activityName = 'Covariate analysis';
activityDescription = 'Covariate analysis of MSBB BM 36 RNASeq samples';

thisFileName <- 'MSSM_BM_36_RNASeq.Rmd'

# Github link
thisRepo <- getRepo(repository = "th1vairam/Brain_Reg_Net", ref="branch", refName='AMPAD')
thisFile <- getPermlink(repository = thisRepo, repositoryPath=paste0('code/Rmd/',thisFileName))
```
Data were obtained from AMP-AD portal of MSSM, and following brain regions were analysed for differential expression between case and control:
  | Region | Name                        | 
  | :----- | --------------------------- | 
  | BM_36  | Parahipocampal Gyrus (PHG)  |

  * BM 36: Ectorhinal area 36 is a subdivision of the cytoarchitecturally defined temporal region of cerebral cortex.

@@

METADATA = left_join(METADATA %>%
                       dplyr::mutate(ID = gsub('hB_RNA_','',NewBarcode),
                                     ID = as.numeric(ID)),
                     METADATA_TECHNICAL %>%
                       dplyr::select(BB, BM.44.Barcode, BM36.Fnl, BM22.Fnl, BM10.Fnl, PMI, RACE, 
                                     AOD, CDR, SEX, NP.1, PlaqueMean, bbscore) %>%
                       dplyr::rename(BM_44 = BM.44.Barcode,
                                     BM_10 = BM10.Fnl,
                                     BM_22 = BM22.Fnl,
                                     BM_36 = BM36.Fnl) %>%
                       tidyr::gather(BrainRegion, ID, -BB, -PMI, -RACE, 
                                     -AOD, -CDR, -SEX, -NP.1, -PlaqueMean, -bbscore) %>%
                       filter(!is.na(ID)) %>%
                       dplyr::mutate(ID = as.numeric(ID))) %>%
  dplyr::filter(BrainRegion == 'BM_36')
rownames(METADATA) = METADATA$NewBarcode

@@

### Store files in synapse
```{r synapse.store, include=FALSE, eval=TRUE, cache=FALSE}
# Code
CODE <- Folder(name = "MSBB BM 36 RNASeq", parentId = parentId)
CODE <- synStore(CODE)
